Identifying 15-minute neighbourhoods with complete caring potential

### 2024-10-04 paper/Manuscript.qmd
Proofreading with Anastasia

```{r library-setup}
library(biscale)
library(cowplot)
library(magick)
library(dplyr)
library(flextable)
library(ftExtra)
library(glue)
library(here)
library(mapview)
library(pander)
library(scales)
library(sf)
library(tmap)
library(tmaptools)
library(gt)
#install.packages("gtExtras")
library(gtExtras)
```

>>>>

```{r library-setup}
library(biscale)
library(cowplot)
library(magick)
library(dplyr)
library(flextable)
library(ftExtra)
library(glue)
library(here)
library(mapview)
library(pander)
library(scales)
library(sf)
library(tidyr)
library(tmap)
library(tmaptools)
library(gt)
#install.packages("gtExtras")
library(gtExtras)
```
